---
title: "BIOL2010 prac series one"
output: 
  learnr::tutorial:
    progressive: TRUE
    language:
      en:
        button:
          continue: "continue"
          previoustopic: "go back"
          nexttopic: "continue"
runtime: shiny_prerendered
---

```{r setup, include=FALSE}

library(DT)
library(learnr)
library(knitr)
library(readxl) 
library(tidyverse)

dat_sample <- read_excel(path = "data/biol2010-prac-1-data-2026.xlsx",
                         sheet = "sample_level")

dat_macroinvert <- read_excel(path = "data/biol2010-prac-1-data-2026.xlsx",
                              sheet = "macroinvert_level")

```

## Visions of data
###
Have a look at your aquatic macroinvertebrate data below!

```{r view-data-macroinvert, echo=FALSE}

datatable(dat_macroinvert,
          rownames = FALSE,
          options = list(dom = "lpt",
                         scrollX = TRUE))

```
<br>
Do you think this data is useful...and ready to use?

###
Ah, much nicer in a summarised form.

```{r view-data-sample, echo=FALSE}

datatable(dat_sample,
          rownames = FALSE,
          options = list(dom = "lpt",
                         scrollX = TRUE))

```
<br>
What plot could we use to visualise our data?

###
Let's turn your plot idea into code! 

```{r plot-points, exercise=TRUE}

ggplot(data = dat_sample) +
  geom_SOMETHING(aes(x = PREDICTOR_VARIABLE,
                      y = RESPONSE_VARIABLE,
                      ymin = SOMETHING,
                      ymax = SOMETHING),
                  colour = "orange",
                  size = 2, 
                  linewidth = 0.5) +
  scale_x_continuous(name = "something abiotic, I swear") +
  scale_y_continuous(name = "goated (?) macroinvert community-level descriptor",
                     limits = c(0, NA)) +
  theme_classic() 

```

Once you've fixed the code above, you should now be looking at a _pretty_ plot --- but it's still missing a key scientific element.

###
Let's add a line to your plot --- __add a `geom_smooth(...)` layer in the code above__.

You should now have a plot that is both _pretty_ and _scientifically complete_ --- how thrilling. Take a moment to copy this into your practical journal. 

## Building a relationship 
###
How can we tell if there's a _significant_ relationship between nitrogen (total nitrogen concentration) and aquatic macroinvertebrates (community SIGNAL sensitivity score)? 

```{r stats-linear-model, exercise=TRUE}

scatter_plot_vibes <- SOME_TEST(RESP_VAR ~ PRED_VAR,
                         data = dat_sample)

summary(scatter_plot_vibes)

```

###
What is the key conclusion from this statistical evidence?

Can you confidently use the numbers in this evidence to describe the relationship?

## Moving out

You have now successfully:

* made a good figure; 
* written a caption for it;
* conducted a statistical analysis; and
* written an intepretation for it.

Before exiting this tutorial, ensure that you have copied out anything required for your practical journal.
